---
title: "M3-project"
date: "24 nov 2019"
output:
  html_document:
    code_folding: hide
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---
# Introduction

# Problem

# Data desciption

# Multiple input model

## Data

We start by cleaning the environment.

```{r, include=FALSE}
#Cleaning the environment
rm(list=ls())
```

And then we'll import Keras, which is essential for the anaysis. You have to use "install_keras" if you're installing Keras for the first time.

```{r}
devtools::install_github("rstudio/keras", force = TRUE)
library(keras)
#install_keras()
```

And then we'll load a bunch of other packages.

```{r}
#Loading packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(knitr,
               readr,
               rmarkdown, 
               tidyverse,
               dplyr,
               broom,
               keras,
               drat,
               reticulate,
               SciencesPo,
               caret
               )
```

And now we can download the data from the Github.

```{r}
data = read_csv("https://github.com/emanhamed/Houses-dataset")
```

```{r}
files <- list.files(path = "C:/Users/Michael Thomsen/Desktop/Houses-dataset-master/Houses Dataset", 
                    pattern = "*.jpg", full.names=TRUE)
images <- lapply(files,FUN = simplify )
house_info <- read_table2("C:/Users/Michael Thomsen/Desktop/Houses-dataset-master/Houses Dataset/HousesInfo.txt")
```


```{r}
files <- list.files(path = "C:/Users/Emma/OneDrive/Universitetet/Houses-dataset-master/Houses-dataset-master/Houses-dataset/", 
                    pattern = "*.jpg", full.names=TRUE)
images <- lapply(files,FUN = simplify )
house_info <- read_table2("C:/Users/Emma/OneDrive/Universitetet/Houses-dataset-master/Houses-dataset-master/Houses-dataset/HousesInfo.txt")
```

## Preprocess of numeric 

We'll start with looking at the distribution of the data, here number of bedrooms, bathrooms, zipcode. The area is differently distributed, so there's not much to look in to. We'll start with the bedrooms.

```{r}
table(house_info$Bedrooms)
```
Here we can see that most of the houses have 2 to 4 bedrooms. And now the bathrooms.

```{r}
table(house_info$Bathrooms)
```
And most of the houses have 2 to 3 badrooms. 

```{r}
table(house_info$Zipcode)
```
Here we can see that some zipcodes only are represented by 1 or 2 houses while other have up to 100 houses. 

```{r}
index = createDataPartition(house_info, p=0.75)

training = house_info[index,]
test = house_info[-index,]
```


```{r}
normalize()
```



## Preprocess of images



